Road traffic sound level estimation from realistic urban sound mixtures by Non-negative Matrix Factorization

### 2018-03-05 paper/gloaguenAppliedNMF.tex
add cumulative times

The urban sound scenes are taken from 76 recordings from 2 to 5 min, achieved in the \nth{13} district of Paris (France) at 19 different locations \footnote{Recordings were made as part of the Grafic project funded by Ademe}, which cover four various sound environments (Figure \ref{fig:map_grafic}), see Figure \ref{fig:map_grafic}. A complete description of the experimental protocol can be found in \cite{aumond_modelling_2017}. Two of the 76 recordings are rejected for the analysis because the audio files were corrupted, resulting in 74 valid audio files assumed as representative of the variety of sound environments. The recordings are listened and categorized within four different sound environments, as proposed in \cite{can_describing_2015}: park (P, 8 audio files), quiet street (Q, 33 audio files), noisy street (N, 24 audio files) and very noisy street (vN, 9 audio files). Then, each audio file is annotated, noting the start and end time of each sound event along with its sound class. The aim of the annotation phase is next to transcribe the recordings, in order to obtain simulated sound scenes with the same distribution of sound events as the recordings and therefore as close as possible to the realistic scenes.

>>>>

The urban sound scenes are taken from 76 recordings from 2 to 5 min, achieved in the \nth{13} district of Paris (France) at 19 different locations \footnote{Recordings were made as part of the Grafic project funded by Ademe}, which cover four various sound environments (Figure \ref{fig:map_grafic}), see Figure \ref{fig:map_grafic}. A complete description of the experimental protocol can be found in \cite{aumond_modelling_2017}. Two of the 76 recordings are rejected for the analysis because the audio files were corrupted, resulting in 74 valid audio files assumed as representative of the variety of sound environments. The recordings are listened and categorized within four different sound environments, as proposed in \cite{can_describing_2015}: park (P, 8 audio files with a cumulative duration of 16min01), quiet street (Q, 33 audio files with a cumulative duration of 77min27), noisy street (N, 24 audio files with a cumulative duration of 56min10) and very noisy street (vN, 9 audio files with a cumulative duration of 21min42). Then, each audio file is annotated, noting the start and end time of each sound event along with its sound class. The aim of the annotation phase is next to transcribe the recordings, in order to obtain simulated sound scenes with the same distribution of sound events as the recordings and therefore as close as possible to the realistic scenes.
